PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-24 qfenv_paper/qf_environment.tex
more qf section additions

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating quiescent fraction - the fraction of galaxies that have depleted their star-formation. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution over redshift for galaxies in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE), that operate on the scale of our environment measure.

@@

Most noticeably, $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment. In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation. With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{blanton09a}).

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments and over our mass range $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly agree with the observed decline of global star-formation in the universe (\cite{hopkins06a}).

@@

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M}_{*} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ values at the lowest and highest overdensity values, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our SDSS sample low and high density environment $f_{\rm{Q}}$ at the lowest mass bin $\rm{log} \; \mathcal{M} \sim 10.2$. At higher mass ranges, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}. \cite{Baldry:2006aa} using project neighbor density environment measures ($\rm{log} \;  \Sigma$) in order to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurement makes a direct comparison unclear, $f_{\rm{Q}}$ for higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} is roughly $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment. Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which agrees with our low density environment $f_{\rm{Q}}$.

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments. Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} illustrates that there is a significant difference between classifying the quenched population using color and SFR: $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by $\sim 0.2$. Although the difference does not propagate evenly for the environment classification, once we approximately account for the difference $f_{\rm{red}}$ in \cite{Kovac:2014aa} is generally consistent with our $f_{\rm{Q}}$ results for both high and low density environments. %Highlight that PRIMUS has more statistics?

Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in the section. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution for lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over $0.4 \lesssim z \lesssim 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each panels in Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern. In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}
%fiducial mass may be 11.0 depending on what we want.

@@

Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa}. Therefore, for $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions.

The same fitting was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments increases by $\sim 0.2$ from as redshift decreases from $z \sim 0.7$ to $z \sim 0.1$. 
This suggests that the total amount of $f_{\rm{Q}}$ evolution at $\mathcal{M} \sim This further supports our previous suggestion that there is little mass dependence in our $f_{\rm{Q}}$ evolution. Although our sample from PRIMUS provides larger statistics, due to the limited mass ranges probed in our mass-complete sample ($\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.

In addition, throughout the redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment.

From Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier. More importantly it quantifies the total evolution of $f_{\rm{Q}}$ since $z \sim 0.8$ for both low and high density environments. Remarkably, the total evolution of $f_{\rm{Q}}$ remains constant for both environments. In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show no strong environment dependence.

%Discuss how this is not due to contamination by environment classifications.

% The "color-mass" relation holds for both low and high environment galaxies. While others in literature (Cucciati et al. 2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data. Although this could be due to the contamination in our environment measurements since there are large redshift errors.

>>>>

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE).

@@

Most noticeably in Figure \ref{fig:qf}, $f_{\rm{Q}}$ increases monotonically as a function of mass at all redshift bin and environment. In other words, for all subsamples, galaxies in higher mass bins are more likely to have quenched its star-formation. With the roughly linear correlation between galaxy SFR to galaxy color and morphology, we find that this trend reflects the well established color-mass and morphology-mass relations: more massive galaxies are more likely to be red or early-type (\cite{blanton09a}).

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly agree with the observed decline of global star-formation in the universe (\cite{hopkins06a}). %Maybe Stacey et al. 2014 is relevant here?

@@

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}/f_{\rm{red}}$ measurements for SDSS galaxies as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$). At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}. \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurements make a direct comparison unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$) in \cite{Baldry:2006aa} $f_{\rm{Q}} \sim 0.6$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.9$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, in agreement our high density environment. Likewise, for lower environments in \cite{Baldry:2006aa} ($\rm{log} \; \Sigma < -0.4$) $f_{\rm{Q}} \sim 0.4$ at $\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}$ and $f_{\rm{Q}} \sim 0.8$ at $\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}$, which also agree with our low density environment $f_{\rm{Q}}$.

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments. Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference evenly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.

Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in the section. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.

In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}

@@

Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa}. For $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions. %Color-density dependence in Cucciati?

The same fitting procedure was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, just as \ref{fig:qffit}. Increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ also does not change the total evolution for either environments. In contrast, as mentioned above, \cite{Iovino:2010aa} finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$. Furthermore, changing the fiducial mass does not significant change the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ between the environments. This is again in disagreement with \cite{Iovino:2010aa}, which finds a significant redshift dependent difference in $f_{\rm{blue}}$ between group and isolated galaxies at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, but finds no difference at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$. As suggested earlier, our $f_{\rm{Q}}$ results show little mass dependence in our $f_{\rm{Q}}$ evolution. Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.

Finally, from Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier. More importantly, it quantifies the total evolution of $f_{\rm{Q}}$ since $z \sim 0.8$ for both low and high density environments. Remarkably, the $f_{\rm{Q}}$ evolves by the same amount for both environments. In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show little environment dependence. This disagrees with the $f_{\rm{blue}}$ results from \cite{Iovino:2010aa}, which show a clear distinction between group and isolated galaxies. In \cite{Iovino:2010aa}, $f_{\rm{blue}}$ for isolated galaxies decrease much faster than $f_{\rm{blue}}$ for group galaxies. At $\mathcal{M} \sim 10.5$, \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ for isolated galaxy decreases by 0.3 from z~0.6 to 0.3, while for $f_{\rm{blue}}$ for group galaxies only decrease by 0.1 in the same redshift limit, showing a clear dependence in environment. 
% Considering our definition of environment may be susceptible to contamination, we considered more stringent classification of both low and high density environments. However,
